A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2025-07-20 paper/paper.tex
No more numbering of Appendix

Types are organized in a hierarchy of universes written $\Type_m$ for $m$ a natural number. The main types in type theory are the type of dependent pairs, written $\Sigma a : A.\,B(a)$, the type of dependent functions, written $\Pi a : A.\,B(a)$, for $A$ a type and $B(a)$ a type dependent on the inhabitant $a$ of $A$, and the type of propositional equalities, written $t = u$. As a notation, the type of dependent pairs when $B$ is not dependent on $A$ is shortened into $A \times B$ and the type of dependent functions when $B$ is not dependent on $A$ is written $A \rightarrow B$. We assume our type theory to also include a distinguished singleton type, written $\unittype$, and with inhabitant $\unitpoint$, the type of boolean values, and the type of natural numbers. We write $\hd$ and $\tl$ the projections of dependent pairs, and $\refl$ for reflexivity. Logical propositions being types themselves, we use $\Pi$ to represent universal quantification and $\Sigma$ to represent existential quantification. We also assume that our type theory includes a coinductively-defined notion of dependent streams described in Appendix \ref{app:depstream}.

@@

\newpage
\appendix
\fancyhead[L]{\footnotesize\textcolor{gray80}{{\MakeUppercase{Appendix}}}}
\section*{Appendix: Definition of dependent stream\label{app:depstream}}

>>>>

Types are organized in a hierarchy of universes written $\Type_m$ for $m$ a natural number. The main types in type theory are the type of dependent pairs, written $\Sigma a : A.\,B(a)$, the type of dependent functions, written $\Pi a : A.\,B(a)$, for $A$ a type and $B(a)$ a type dependent on the inhabitant $a$ of $A$, and the type of propositional equalities, written $t = u$. As a notation, the type of dependent pairs when $B$ is not dependent on $A$ is shortened into $A \times B$ and the type of dependent functions when $B$ is not dependent on $A$ is written $A \rightarrow B$. We assume our type theory to also include a distinguished singleton type, written $\unittype$, and with inhabitant $\unitpoint$, the type of boolean values, and the type of natural numbers. We write $\hd$ and $\tl$ the projections of dependent pairs, and $\refl$ for reflexivity. Logical propositions being types themselves, we use $\Pi$ to represent universal quantification and $\Sigma$ to represent existential quantification. We also assume that our type theory includes a coinductively-defined notion of dependent streams described in the Appendix.

@@

\newpage
\appendix
\fancyhead[L]{\footnotesize\textcolor{gray80}{{\MakeUppercase{Appendix}}}}
\section*{Appendix: Definition of dependent stream}
